Bird beak's elaboration and innovation

### 2022-02-04 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE, results = 'hide', message = FALSE, warning = FALSE}
## Run the analyses between groups
super_results_between <- dispRity.covar.projections(superorder_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses between groups
order_results_between <- dispRity.covar.projections(order_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses of groups on the phylogeny
super_results_phylo <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses of groups on the phylogeny
order_results_phylo <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
super_results_within <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
order_results_within <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
shapespace_allbirds_lvl_superorder_order_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(shapespace_allbirds_lvl_superorder_order_results_list, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_centred.rda")
```

```{r, echo = FALSE}
## Quick load
# load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_uncentred.rda")
# results_cent <- shapespace_allbirds_lvl_superorder_order_results_list
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_centred.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)
```

@@

    if(!missing(tree)) {
        # op <- par(mfrow = c(1,2))
        #c(bottom, left, top, right); c(5, 4, 4, 2) + 0.1
        par(mar = c(5, 4, 4, 0)+0.1)   
    }

>>>>

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = TRUE, results = 'hide', message = FALSE, warning = FALSE}
## Run the analyses between groups
super_results_between <- dispRity.covar.projections(superorder_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses between groups
order_results_between <- dispRity.covar.projections(order_shapespace,
                                             type = "groups",
                                             base = "phylogeny",
                                             verbose = TRUE,
                                             output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses of groups on the phylogeny
super_results_phylo <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)

## Run the analyses of groups on the phylogeny
order_results_phylo <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
super_results_within <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
## Run the analyses groups on themselves
order_results_within <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            verbose = TRUE,
                                            output = c("position", "distance"), centre = TRUE, abs = TRUE)
shapespace_allbirds_lvl_superorder_order_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(shapespace_allbirds_lvl_superorder_order_results_list, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
```

```{r, echo = FALSE, eval = FALSE}
## Getting the plotting data
ploting_data <- list("median_elaborations" = apply(get.disparity(get.subsets(super_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(super_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" =  get.disparity(dispRity(get.subsets(superorder_shapespace, subsets = "phylogeny"), metric = centroids, centroid = 0)),
                     "consensus_tree"      = tree)

## Save all that as a list
save(ploting_data, file = "ploting_data.rda")
```

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)
```

@@

    if(!missing(tree)) {
        op <- par(mfrow = c(1,2))
        #c(bottom, left, top, right); c(5, 4, 4, 2) + 0.1
        par(mar = c(5, 4, 4, 0)+0.1)   
    }
